---
title: "Robust Regression and Outlier Detection" 
subtitle: "Chapter 2: Simple Regression"
institut: "umwelt und natürliche ressourcen"
lang: de
thesis-type: "Projektarbeit 2"
bibliography: references.bib
author: 
  - Peter J. Rousseeuw
  - Annick M. Leroy
date: "1987-10-19"
format: 
  zhaw-lsfm-typst: default
execute:
  echo: false
---



# Example 4: Brain and Weight Data

Table 7 presents the brain weight (in grams) and the body weight (in
kilograms) of 28 animals. (This sample was taken from larger data sets in
@weisberg1980 and @jerison1973.) It is to be investigated whether a larger
brain is required to govern a heavier body. 

A clear picture of the relationship between the logarithms (to the base
10) of these measurements is shown in Figure 7. This logarithmic 
transformation was necessary because plotting the original measurements
would fail to represent either the smaller or the larger measurements.
Indeed, both original variables range over several orders of magnitude. A
linear fit to this transformed data would be equivalent to a relationship of
the form


$$ \hat{y} =\hat{\theta}_2^{\prime} x^{\hat{\theta}_1}  $$


```{r}
#| tbl-cap: "Table 7: Brain and body weights of 28 animals."
#| label: tbl-animals

library(MASS)

Animals <- MASS::Animals

knitr::kable(Animals)

```


```{r}
#| label: fig-brain-body
#| fig-cap: "Logarithmic brain weight versus logarithmic body weight for 28 animals with LS (dashed line) and RLS fit (solid line)."


plot(log10(brain) ~ log10(body), data = Animals, 
     xlab = "Logarithmic body weight (kg)", 
     ylab = "Logarithmic brain weight (g)", 
     pch = 19, col = "blue", cex = 1.5)


```






